Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2015-12-16 ijar-npb-ms.tex
minor work on secs 3 and 4

\newcommand{\ber}{\operatorname{Bernoulli}} 
\newcommand{\bin}{\operatorname{Binomial}}
\newcommand{\be}{\operatorname{Beta}} 
\newcommand{\bebin}{\operatorname{Beta-binomial}}

@@

The \emph{survival signature} for such a system, denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,m_k$ 
for $k=1,\ldots,K$, is defined as the probability for the event that the system functions given that \emph{precisely} $l_k$ of its 
$m_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$ \citep{2012:survsign}.
Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$, such that $\Rsys(t) = P(\Tsys > t)$
can be calculated using the law of total probability:
\begin{align*}
P(\Tsys > t)
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K) \\
 &  \hspace*{24ex}                        \times P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \,,
%                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
\end{align*}
where $C^k_t \in \{0, 1, \ldots, m_k\}$ denotes
the random number of components of type $k$ functioning at time $t$.

For calculating the survival signature based on the structure function, observe that
there are $\binom{m_k}{l_k}$ state vectors $\underline{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
denote the set of these state vectors for components of type $k$ and let $S_{l_1,\ldots,l_K}$ denote the set of 
all state vectors for the whole system for which $\sum_{i=1}^{m_k} x^k_i = l_k$, $k=1,\ldots,K$. Due to the 
exchangeability assumption for the failure times of the $m_k$ components of type $k$, all the state vectors 
$\underline{x}^k \in S^k_{l_k}$ are equally likely to occur, hence \citep{2012:survsign}
\begin{align}
\label{eq:surv-sig}
\Phi(l_1,\ldots,l_K)
 &= \left[ \prod_{k=1}^K \binom{m_k}{l_k}^{-1} \right] \times \sum_{\underline{x} \in S_{l_1,\ldots,l_K}} \phi(\underline{x})\,.
\end{align}
%
%Let $C^k_t \in \{0,1,\ldots,m_k\}$ denote the number of components of type $k$ in the system that function at time $t>0$.
%Then, for system failure time $\Tsys$,
%\begin{align*}
%P(\Tsys > t) &= \Rsys(t) = \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K}  \Phi(l_1,\ldots,l_K) P\Big(\bigcap_{k=1}^K \{C^k_t = l_k\}\Big)\,.
%\end{align*}
It should be emphasized that when using the survival signature,
there are no restrictions on dependence of the failure times of components of different types,
as the probability $P(\bigcap_{k=1}^K \{C^k_t = l_k\})$ can take any form of dependence into account,
for example one can include common-cause failures quite straightforwardly into this approach \citep[see][]{CCM15}.
However, there is a substantial simplification
if one can assume that the failure times of components of different types are independent,
and even more so if one can assume that the failure times of components of type $k$ 
are conditionally independent and identically distributed with CDF $F_k(t)$.
With these assumptions, we get
\begin{align*}
\Rsys(t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \left[ \Phi(l_1,\ldots,l_K)
            \prod_{k=1}^K \left( \binom{m_k}{l_k} [F_k(t)]^{m_k-l_k} [1-F_k(t)]^{l_k} \right) \right]\,.
\end{align*}
We will employ both assumptions in this paper,
such that $C^k_t$ is Beta-Binomially distributed,
giving us a closed form expression for $P(C^k_t = l_k)$ for all $t$, $k$, and $l_k$.

@@

The random failure time of component number $i$ of type $k$ is denoted by $T^k_i$, $i = 1, \ldots m_k$.
The failure time distribution can be written in terms of the cdf $F^k(t) = P(T^k_i \le t)$,
or in terms of the reliability function $R^k(t) = P(T^k > t) = 1 - F^k(t)$,
also known as the survival function.
For a nonparametric description of $R^k(t)$,
we consider a set of time points $t$, $t \in {\cal T} = \{t_1, \ldots, \tmax\}$.

@@

\td{***illustrate discrete distribution with a graph of R, q, h?***}

@@

Having observed the lifetime data $\vec{t}^k = (t^k_1, \ldots, t^k_{n_k})$,
at any fixed time $t \in {\cal T}$ this results in the observation from the Binomial model described above,
$s^k_t = \sum_{i=1}^{n_k} \indic(t^k_i > t)$.
The posterior is then $\ptk \mid s^k_t \sim \be(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
The combination of a Binomial observation model with a Beta prior is often called Beta-binomial model.

The posterior predictive distribution for the number of components surviving at time $t$
of the $m_k$ components in the system, based on the lifetime data and the prior information,
is then a so-called Beta-binomial distribution,
$C^k_t \mid s^k_t \sim \bebin(m_k, \alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
That is, we have
\begin{align*}
P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \alpha^k_t + s^k_t, m_k - l_k + \beta^k_t + n_k - s^k_t)}
                                                    {B(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)} \,,
\end{align*}
where $B(\cdot, \cdot)$ is the Beta function.
This posterior predictive distribution is basically a Binomial distribution
where the functioning probability $\ptk$ takes values in $[0,1]$
with the probability given by the posterior on $\ptk$.

To wrap up, to calculate the system reliability according to ***eqnumber***,
for each component type $k$,
we need lifetime data $\vec{t}^k$,
and have to choose $2 \times |{\cal T}|$ parameters
to specify the prior distribution for the discrete survival function of $T^k_i$.
In total, values for $2 \times |{\cal T}| \times K$ parameters must be chosen.

@@

From the properties of the Beta distribution,
it follows that $\yz = \E[p]$ is the prior expectation for the functioning probability $p$,
and that the higher $\nz$, the more probability weight will be concentrated around $\yz$,
as $\V(p) = \frac{\yz (1-\yz)}{\nz + 1}$.
Furthermore, $\nz$ can be interpreted as a pseudocount or prior strength,
this is clear from the interpretation of $\alpha$ and $\beta$ and \eqref{eq:reparam},
and will be further illustrated below through revisiting the posterior
based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$.

$p \mid s$ is Beta distributed with the updated parameters
\begin{align}
\nn &= \nz + n\,, &
\yn &= \frac{\nz}{\nz + n} \cdot \yz + \frac{n}{\nz + n} \cdot \frac{s}{n}\,,
\label{eq:nyupdate}
\end{align}
so after seeing that $s$ out of $n$ components function (at time $t$),
the posterior mean $\yn$ for $p$ is a weighted average of
the prior mean $\yz$ and $s/n$ (the fraction of functioning components in the data),
with the weights $\nz$ and $n$, respectively.
We see that $\nz$ plays the same role for the prior mean $\yz$
as the sample size $n$ for the observed mean $s/n$,
thus the notion of pseudocount.
Indeed, the higher $\nz$, the higher the weight for $\yz$
in the weighted average calculation of $\yn$,
so $\nz$ gives the strength of the prior as compared to the sample size $n$.
%The parameters $\nz$ and $\yz$ have a more intuitive interprtation,

The Beta-binomial probability mass function (pmf) in terms of the updated parameters $\nn$ and $\yn$,
now again with indicators $t$ and $k$,
is therefore
\begin{align}
P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
                                                    {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \,,
\label{eq:postpredCny}
\end{align}
and the corresponding cumulative mass function (cmf) is given by
\begin{align}
F_{C^k_t\mid s^k_t}(l_k) &= P(C^k_t \le l_k \mid s^k_t) = \sum_{j_k=0}^{l_k} P(C^k_t = j_k \mid s^k_t)\,.
\label{eq:postpredCnycmf}
\end{align}

@@

As was shown in \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
we can have both tractability and meaningful reaction to prior-data conflict
by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
(A detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
corresponds to a Beta prior, thus $\MktZ$ is a set of Beta priors.
The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
obtained from updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
and so can be described efficiently through the set of updated parameters
\begin{align*}
\PktN &= \Big\{ (\nktn, \yktn) \mid (\nktz, \yktz) \in \PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu] \Big\}\,.
\end{align*}
Such rectangular prior parameter sets $\PktZ$ have been shown
to balance desirable model properties and ease of elicitation quite well.
%
For each component type $k$ and time point $t$,
one has to choose only the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
(so $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions characterizing
prior knowledge on the survival function of components of type $k$);
notwithstanding this, the model has favourable inference properties.

@@

In absence of prior-data conflict, 
$\PktN$ shrinks in the $\ykt$ dimension;
how much it shrinks depends on $\nktz \in [\nktzl, \nktzu]$,
leading to the so-called spotlight shape depicted in Figure***.
As $\yktn$ gives the posterior expectation for the functioning probability $p_t^k$,
shorter $\yktn$ intervals mean more precise knowledge about $p_t^k$.
Also, the variance interval for $p_t^k$ will decrease
as the Beta distributions in $\MktN$ will be more pointed
due to the increase of $\nktz$ to $\nktn$.s

@@

@@

In this near-noninformative setting, the choice of $\nktzl$ is not relevant,
as both $\yktnl$ and $\yktnu$ are obtained with $\nktzu$;
indeed $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
$\frac{s^k_t}{n_k} \in [\yktzl, \yktzu]$ for all $t \in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
Logically, one cannot have prior-data conflict in case of prior near ignorance.

@@

To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
we now need to minimise and maximise Equation~*** over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
where the posterior predictive probabilities for $C^k_t$ are given by the beta-binomial pmf \eqref{eq:postpredCny}.
It turns out that we need to optimise over $\nktz$ ($k=1,\ldots,K$) only,
as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.

>>>>

\newcommand{\ber}{\operatorname{Bernoulli}} 
\newcommand{\bin}{\operatorname{Binomial}}
\newcommand{\be}{\operatorname{Beta}} 
\newcommand{\bebin}{\operatorname{Beta-Binomial}}

@@

The \emph{survival signature} for such a system, denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,m_k$ 
for $k=1,\ldots,K$, is defined as the probability for the event that the system functions given that \emph{precisely} $l_k$ of its 
$m_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$ \citep{2012:survsign}.
Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$, such that $\Rsys(t) = P(\Tsys > t)$
can be calculated using the law of total probability:
\begin{align}
\label{eq:rsyswithsurvsign}
P(\Tsys > t)
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K) \nonumber\\
 &  \hspace*{24ex}                        \times P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \,,
%                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
\end{align}
where $C^k_t \in \{0, 1, \ldots, m_k\}$ denotes
the random number of components of type $k$ functioning at time $t$.

For calculating the survival signature based on the structure function, observe that
there are $\binom{m_k}{l_k}$ state vectors $\underline{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
denote the set of these state vectors for components of type $k$ and let $S_{l_1,\ldots,l_K}$ denote the set of 
all state vectors for the whole system for which $\sum_{i=1}^{m_k} x^k_i = l_k$, $k=1,\ldots,K$. Due to the 
exchangeability assumption for the failure times of the $m_k$ components of type $k$, all the state vectors 
$\underline{x}^k \in S^k_{l_k}$ are equally likely to occur, hence \citep{2012:survsign}
\begin{align}
\label{eq:surv-sig}
\Phi(l_1,\ldots,l_K)
 &= \left[ \prod_{k=1}^K \binom{m_k}{l_k}^{-1} \right] \times \sum_{\underline{x} \in S_{l_1,\ldots,l_K}} \phi(\underline{x})\,.
\end{align}
%
%Let $C^k_t \in \{0,1,\ldots,m_k\}$ denote the number of components of type $k$ in the system that function at time $t>0$.
%Then, for system failure time $\Tsys$,
%\begin{align*}
%P(\Tsys > t) &= \Rsys(t) = \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K}  \Phi(l_1,\ldots,l_K) P\Big(\bigcap_{k=1}^K \{C^k_t = l_k\}\Big)\,.
%\end{align*}
It should be emphasized that when using the survival signature,
there are no restrictions on dependence of the failure times of components of different types,
as the probability $P(\bigcap_{k=1}^K \{C^k_t = l_k\})$ can take any form of dependence into account,
for example one can include common-cause failures quite straightforwardly into this approach \citep[see][]{CCM15}.
However, there is a substantial simplification
if one can assume that the failure times of components of different types are independent,
and even more so if one can assume that the failure times of components of type $k$ 
are conditionally independent and identically distributed with CDF $F_k(t)$.
With these assumptions, we get
\begin{align*}
\Rsys(t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \left[ \Phi(l_1,\ldots,l_K)
            \prod_{k=1}^K \left( \binom{m_k}{l_k} [F_k(t)]^{m_k-l_k} [1-F_k(t)]^{l_k} \right) \right]\,.
\end{align*}
We will employ both assumptions in this paper,
leading to $C^k_t$ having a Beta-Binomial distribution,
giving us a closed form expression for $P(C^k_t = l_k)$ for all $t$, $k$, and $l_k$.

@@

Let us denote the random failure time of component number $i$ of type $k$ by $T^k_i$, $i = 1, \ldots m_k$.
The failure time distribution can be written in terms of the cdf $F^k(t) = P(T^k_i \le t)$,
or in terms of the reliability function $R^k(t) = P(T^k > t) = 1 - F^k(t)$,
also known as the survival function.
For a nonparametric description of $R^k(t)$,
we consider a set of time points $t$, $t \in {\cal T} = \{t_1, \ldots, \tmax\}$.

@@

\td{***illustrate discrete distribution with a graph of R, f, h?***}

@@

Having observed the lifetime data $\vec{t}^k = (t^k_1, \ldots, t^k_{n_k})$,
at any fixed time $t \in {\cal T}$ this results in the observation from the Binomial model described above,
$s^k_t = \sum_{i=1}^{n_k} \indic(t^k_i > t)$.
The posterior is then $\ptk \mid s^k_t \sim \be(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
The combination of a Binomial observation model with a Beta prior is often called Beta-Binomial model.

The posterior predictive distribution for the number of components surviving at time $t$
of the $m_k$ components in the system, based on the lifetime data and the prior information,
is then a so-called Beta-Binomial distribution,
$C^k_t \mid s^k_t \sim \bebin(m_k, \alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
That is, we have
\begin{align*}
P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \alpha^k_t + s^k_t, m_k - l_k + \beta^k_t + n_k - s^k_t)}
                                                    {B(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)} \,,
\end{align*}
where $B(\cdot, \cdot)$ is the Beta function.
This posterior predictive distribution is basically a Binomial distribution
where the functioning probability $\ptk$ takes values in $[0,1]$
with the probability given by the posterior on $\ptk$.

To wrap up, to calculate the system reliability according to \eqref{eq:rsyswithsurvsign},
for each component type $k$,
we need lifetime data $\vec{t}^k$,
and have to choose $2 \times |{\cal T}|$ parameters
to specify the prior distribution for the discrete survival function of $T^k_i$.
In total, values for $2 \times |{\cal T}| \times K$ parameters must be chosen.

@@

From the properties of the Beta distribution,
it follows that $\yz = \E[p]$ is the prior expectation for the functioning probability $p$,
and that the higher $\nz$, the more probability weight will be concentrated around $\yz$,
as $\V(p) = \frac{\yz (1-\yz)}{\nz + 1}$.
Furthermore, $\nz$ can be interpreted as a pseudocount or prior strength,
this is clear from the interpretation of $\alpha$ and $\beta$ and \eqref{eq:reparam},
and will be further illustrated below through revisiting the posterior
%based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$.
given $s$ of $n$ components functioning.
We have that
$p \mid s$ is Beta distributed with the updated parameters
\begin{align}
\nn &= \nz + n\,, &
\yn &= \frac{\nz}{\nz + n} \cdot \yz + \frac{n}{\nz + n} \cdot \frac{s}{n}\,.
\label{eq:nyupdate}
\end{align}
After seeing that $s$ out of $n$ components function (at time $t$),
the posterior mean $\yn$ for $p$ is a weighted average of
the prior mean $\yz$ and $s/n$ (the fraction of functioning components in the data),
with the weights $\nz$ and $n$, respectively.
We see that $\nz$ plays the same role for the prior mean $\yz$
as the sample size $n$ for the observed mean $s/n$,
thus the notion of pseudocount.
Indeed, the higher $\nz$, the higher the weight for $\yz$
in the weighted average calculation of $\yn$,
so $\nz$ gives the strength of the prior as compared to the sample size $n$.
%The parameters $\nz$ and $\yz$ have a more intuitive interprtation,

The Beta-Binomial probability mass function (pmf) in terms of the updated parameters $\nn$ and $\yn$,
now again with indicators $t$ and $k$,
is therefore
\begin{align}
P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
                                                    {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \,,
\label{eq:postpredCny}
\end{align}
and the corresponding cumulative mass function (cmf) is given by
\begin{align}
F_{C^k_t\mid s^k_t}(l_k) &= P(C^k_t \le l_k \mid s^k_t) = \sum_{j_k=0}^{l_k} P(C^k_t = j_k \mid s^k_t)\,.
\label{eq:postpredCnycmf}
\end{align}

@@

As was shown by \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
we can have both tractability and meaningful reaction to prior-data conflict
by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
(A detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
corresponds to a Beta prior, thus $\MktZ$ is a set of Beta priors.
The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
This element-by-element updating may seem ad-hoc, but can be rigorously justified
as ensuring coherence \citep[\S ***]{1991:walley}, and was termed ``Generalized Bayes' Rule'' by \citet[\S 6***]{1991:walley}.
Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
obtained from updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
and so can be described efficiently through the set of updated parameters
\begin{align*}
\PktN &= \Big\{ (\nktn, \yktn) \mid (\nktz, \yktz) \in \PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu] \Big\}\,.
\end{align*}
Such rectangular prior parameter sets $\PktZ$ have been shown
to balance desirable model properties and ease of elicitation quite well.
%
For each component type $k$ and time point $t$,
one has to choose only the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
(so $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions characterizing
prior knowledge on the survival function of components of type $k$);
notwithstanding this, the model has favourable inference properties.

@@

In absence of prior-data conflict, 
$\PktN$ shrinks in the $\ykt$ dimension;
how much it shrinks depends on $\nktz \in [\nktzl, \nktzu]$,
leading to the so-called spotlight shape depicted in Figure***.
As $\yktn$ gives the posterior expectation for the functioning probability $p_t^k$,
shorter $\yktn$ intervals mean more precise knowledge about $p_t^k$.
Also, the variance interval for $p_t^k$ will decrease
as the Beta distributions in $\MktN$ will be more pointed
due to the increase of $\nktz$ to $\nktn$.

@@

\td{Figure with $\PN$s and sets of beta cdfs for conflict and no conflict case.}

@@

While for an informative prior the choice of $\nktzl$ is relevant for posterior inferences in case of prior-data conflict,
in a near-noninformative setting, the choice of $\nktzl$ is not relevant,
as both $\yktnl$ and $\yktnu$ are obtained with $\nktzu$;
indeed $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
$\frac{s^k_t}{n_k} \in [\yktzl, \yktzu]$ for all $t \in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
Obviously, one cannot have prior-data conflict in case of prior near ignorance.

@@

To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
we now need to minimise and maximise Equation~\eqref{} over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
where the posterior predictive probabilities for $C^k_t$ are given by the beta-binomial pmf \eqref{eq:postpredCny}.
It turns out that we need to optimise over $\nktz$ ($k=1,\ldots,K$) only,
as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
